\def\swap{\leftrightarrow}
\def\peq{\boxplus}
\def\teq{\otimes}
\def\xor{\oplus}
\def\nimplies{\triangleright}
\def\from{\gets}
\def\real{\mathbb{R}}
\def\rtnl{\mathbb{Q}}
\def\cplx{\mathbb{C}}
\def\setz{\mathbb{Z}}
\def\exp{\mathbb{E}}
\def\f{\mathbb{F}}
\def\N{\mathcal{N}}
\def\E{\mathbb{E}}
\def\zplus{\setz^{+}}
\def\nat{\mathbb{N}}
\def\transpose{^\top}
\def\kleene{^{*}}
\def\const{\mathtt{C}}
\def\p{\partial}
\def\gl{{GL}}
\def\sll{{SL}}
\def\Ub{\mathbf{U}\ }
\def\Sb{\mathbf{S}\ }
\def\vt{\vartheta}
\documentclass[a4paper]{article}
\renewcommand{\thesection}{\arabic{section}}
\renewcommand{\thesubsection}{\alph{subsection}.}
\renewcommand{\labelenumi}{(\alph{enumi})}
\renewcommand{\labelenumii}{(\alph{enumii})}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\renewcommand{\thempfootnote}{\fnsymbol{mpfootnote}}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{euler,beton}
\usepackage{algorithmic}
\usepackage{fontspec}
\usepackage[agsm]{harvard}
\usepackage{hyperref}
\usepackage{xunicode,xltxtra}
\usepackage{graphicx}
\usepackage{sectsty}
\usepackage{multicol}
\usepackage{stmaryrd}
\usepackage{semantic}
\usepackage{tikz}
%\usepackage{listings}
%\usepackage{verbatim}
\usepackage{color}
%\usepackage{pgf,tikz}
\usepackage{booktabs}
\usepackage{fullpage}%\usepackage[left=3cm,right=3cm,top=2.5cm,bottom=2.5cm]{geometry}
\usepackage{fancyhdr}
\usepackage{qtree}
\tikzset{every tree node/.style={align=center, anchor=north}}
% \usepackage{tikz-qtree-compat}
\usepackage{gb4e}
\usepackage[normalem]{ulem}
\usetikzlibrary{trees,arrows,automata,shapes,positioning,calc}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\lfoot{}
\cfoot{\thepage}
\rfoot{Semantics B \\ Chapters 9,10}
\setmainfont[Ligatures={Common},ItalicFont = Linux Libertine O Italic]{Linux Libertine O}
\providecommand{\abs}[1]{\left\lvert#1\right\rvert}
\providecommand{\norm}[1]{\left\lVert#1\right\rVert}
\providecommand{\tuple}[1]{\left\langle#1\right\rangle}
\providecommand{\max}[1]{\max\left(#1\right)}
\providecommand{\min}[1]{\min\left(#1\right)}
\providecommand{\gen}[1]{\left\langle#1\right\rangle}
\providecommand{\coltwo}[2]{\begin{bmatrix}#1 \\ #2\end{bmatrix}}
\providecommand{\msfour}[4]{\begin{bmatrix}#1 & #2 \\ #3 & #4\end{bmatrix}}
\providecommand{\msnine}[9]{\begin{bmatrix}#1 & #2 & #3 \\ #4 & #5 & #6 \\ #7 & #8 & #9\end{bmatrix}}
\providecommand{\deduces}{\mathbin{\vdash}}
\providecommand{\ddeduces}{\mathbin{\vdash\!\!\!\dashv}}
\providecommand{\sch}[1]{\mathcal{#1}}
\providecommand{\dimplies}{\Leftrightarrow}
\providecommand{\ceil}[1]{\left\lceil#1\right\rceil}
\providecommand{\floor}[1]{\left\lfloor#1\right\rfloor}
\renewcommand{\and}{\mathbin{\&}}
\renewcommand{\implies}{\Rightarrow}
\renewcommand{\impliedby}{\Leftarrow}
\DeclareMathOperator{\sech}{sech}
\DeclareMathOperator{\adj}{adj}
\DeclareMathOperator{\infi}{inf}
\DeclareMathOperator{\supre}{sup}
\DeclareMathOperator{\round}{round}
\DeclareMathOperator{\pascal}{pascal}
\DeclareMathOperator{\dom}{domain}
\DeclareMathOperator{\st}{s.t }
\DeclareMathOperator{\argmax}{arg\ max}
\providecommand{\Resc}{\Res\kleene}
\newtheorem{lemma}{Lemma}
\newtheorem{sublemma}{Sublemma}
\sectionfont{\pagebreak[3]}
\subsectionfont{\pagebreak[2]}
\reservestyle{\csyms}{\mathcal}
\csyms{A,B,C,D}
\mathlig{|}{\mid}
\mathlig{==}{\equiv}
\mathlig{~>}{\rightsquigarrow}
\mathlig{~=}{\approx}
\mathlig{~}{\lnot}
\mathlig{|->}{\mapsto}
\mathlig{||-}{\Vdash}
\mathlig{<F>}{\langle{}F \rangle}
\mathlig{|/=}{\nvDash}
\mathlig{[|}{\llbracket}
\mathlig{|]}{\rrbracket}

\title{H\&K Chapters 9, 10}
\author{Sohum Banerjea, Andrew Hedding, Lisa Hofmann}
\date{\today}


\begin{document}

\maketitle

\section{Bound and referential pronouns}
\subsection{Deixis/Anaphora vs Reference/Binding}
\begin{itemize}
\item Describing pronoun behaviour
  \begin{enumerate}
  \item (After John has left the room) I am glad he\textsuperscript{deictic, referring} is gone.
  \item No one likes John. Let's not invite him\textsuperscript{anaphoric, referring}.
  \item Every man is to clean his\textsuperscript{anaphoric, bound} uniform.
  \end{enumerate}
\item These are clearly different categorisations of pronoun behaviour
\item But referring/bound is a useful \emph{semantic} categorisation, in a way deixis/anaphora is not.
\item Bound pronouns use coindexing at syntax and are thus bound semantically in the generated LF
\item Referring pronouns work via salience, and are thus free variables in the generated LF
  \begin{itemize}
  \item (whether salience is extralinguistic or because the anaphora has been recently mentioned)
  \end{itemize}
\end{itemize}

\subsection{Referring pronouns}
\begin{itemize}
\item Referring pronouns thus need the utterance context to provide their variables for the LF to be
  well-defined
\item Capture this by saying that $g$ needs to define any free variables in the LF (``appropriateness'')
\item You can even capture pronoun features, by extending $D_e$ and $D_t$ with failure (call it $\#$) and the
  language with conditioning

  \Tree[. [.{[third person]} ] [. [.{[feminine]} ] [. [.{[singular]} ] [.{she\textsubscript{1}} ] ] ] ]
\item $[|1|] = [|\lambda x.\ \lambda y.\ x|]$ and $[|0|]= [|\lambda x.\ \lambda y.\ y|]$ (Church encoding of booleans)
\item $[feminine] ~> \lambda x_e.\ [\textsc{female}_{et}(x)](x)(\#)$
\end{itemize}

\subsection{Bound pronouns}
\begin{itemize}
\item Bound pronouns show up in quantifiers, as we've seen
\item But there are many other cases where bound variables show up in LFs
\item \Tree[. [. [.{The} ] [. [.{[dog]\textsubscript{x}} ] [.{that greeted his\textsubscript{x} master} ] ] ] [.{was fed}
  ] ]
\item The bound variable analysis here correctly generates ``that greeted his master'' as a reflexive
  condition to be satisfied under the definiteness claim
\item Any referential analysis would have ``his master'' refer to one particular person in the utterance
  context, and thus never generate the reflexive condition
\item The theory also predicts ``invisible'' ambiguity, between bound and free variables, in some cases
  \begin{itemize}
  \item John hates his\textsubscript{x} father
    \begin{itemize}
      \item The free variable can easily pick out John; he's salient by virtue of having just been mentioned!
    \end{itemize}
  \item $\lbrack$John$\rbrack$\textsuperscript{x} t\textsubscript{x} hates his\textsubscript{x} father
  \end{itemize}
  \item Or is it so invisible?…
\end{itemize}

\section{Pronouns and Ellipsis}
\begin{itemize}
\item In this section, H \& K describe two types of ellipsis: VP Ellipsis and Bare Argument Ellipsis (aka ``stripping'')
\item Ellipsis provides a straightforward argument to demonstrate that pronouns can be ``free'' (referring to a salient entity in context) or bound by the trace of QR.  
\item This indicates that the ``invisible'' ambiguity predicted by the theory is supported by empirical evidence.
\end{itemize}
\subsection{VP Ellipsis}
\begin{itemize}
\item VP ellipsis involves deleting a VP that has an identical antecedent. For example:
\end{itemize}
\Tree 		[.S
				[.
					[.Laura ]
					[.
						[.$\lbrack$\textsc{past}$\rbrack$ ]
						[.VP
							[.leave ]
							[.Texas ]
						]		
					]
				]	
				[.
					[.but ]
					[.
						[.Lena ]
						[.
							[.didn't ]
							[.$\langle$VP$\rangle$
								[.$\langle$leave$\rangle$ ]
								[.$\langle$Texas$\rangle$ ]
							]
						]
					]
				]
			]		
\begin{itemize}
\item The identity of the two VPs at LF licenses optional deletion of the second VP on the PF branch (indicated by $\langle$$\rangle$ in the trees in this handout). 
\begin{itemize}
\item \emph{LF Identity Condition on Ellipsis}: A constituent may be deleted at PF only if it is a copy of another constituent at LF.	
\end{itemize}
\item Crucially, the elided material must have an identical LF representation, not only an identical surface string. 
\item Elided material cannot be interpreted with a different scope reading than its antecedent.
\begin{itemize}
\item Laura showed a drawing to every teacher, but Lena didn't.
\end{itemize}
\item \textbf{This cannot be interpreted as:} Laura showed every teacher some drawing (not necessarily the same one) and Lena didn't show exactly one drawing to every teacher (but maybe she showed each teacher a different drawing). 
\end{itemize}
\subsection{Bare Argument Ellipsis}
\begin{itemize}
\item Bare Argument Ellipsis involves eliding an entire sentence after one argument has been topicalized. The corresponding argument in the antecedent must be QR'ed in order to create an identical LF for ellipsis. For example:	
\end{itemize}			
\Tree 	[.S
			[.
				[.$\lbrack${the milk}$\rbrack^x$ ]
				[.S
					[.Laura ]
					[.
						[.drank ]
						[.$x$ ]
					]	
				]		
			]		
			[.	
				[.{or perhaps} ]
				[.
					[.$\lbrack${the juice}$\rbrack^x$ ]
					[.$\langle$S$\rangle$
						[.$\langle$Laura$\rangle$ ]
						[.$\langle$VP$\rangle$
							[.$\langle$drank$\rangle$ ]
							[.$\langle x\rangle$ ]
						]
					]
				]
			]
		]
\begin{itemize}
\item Once \emph{the milk} has been QR'ed, then there are two identical subparts of the tree (\emph{Laura drank x}). This licenses ellipsis.	
\end{itemize}
		
\subsection{Referential Pronouns}
\begin{itemize}
\item Elided phrases can also contain pronouns. The interpretation of ellipsis demonstrates that pronouns can be bound by an anaphor, or they can be free and refer to a salient entity. 
\item \textbf{Context:} It is Roman's birthday...
\begin{itemize}
\item Phillip went to his office.
\end{itemize}
\item \emph{his} could be interpreted as referring to Roman or Phillip. 
\item When ellipsis is added, the bound or free interpretation must be maintained.
\begin{itemize}
\item Phillip went to his office. Marcel didn't.
\end{itemize}
\item \textbf{This cannot mean:} Phillip went to Roman's office and Marcel didn't go to his own office. 
\item The theory of ellipsis developed thus far cannot account for this fact. For example:
\end{itemize}
\begin{multicols}{2}	
\Tree	[.S
			[.Phillip ]
			[.	
				[.$\lbrack$\textsc{past}$\rbrack$ ]	
				[.VP
					[.{go to} ]
					[.{his_x office} ]
				]
			]
		]

\Tree	[.S
			[.$\lbrack$Marcel$\rbrack^x$ ]
			[.	
				[.$x$ ]	
				[.
					[.didn't ]
					[.$\langle$VP$\rangle$
						[.$\langle${go to}$\rangle$ ]
						[.$\langle${his_x office}$\rangle$ ]
					]
				]
			]
		]
\end{multicols}		
\begin{itemize}
\item In this example, \emph{his} is a free variable in the first sentence and it derives its meaning from context. In the second sentence, \emph{his} is bound by Marcel. 
\item This predicts the impossible meaning that Phillip went to Roman's office and Marcel didn't go to his own office.	
\item H \& K solve this problem with the following solution: 
\begin{itemize}
\item No LF representation (for a sentence or multisentential text) must contain both bound occurrences and free occurrences of the same index.
\end{itemize}

\end{itemize}
\subsection{Strict and Sloppy Readings}
\begin{itemize} 
\item Variable binding can also help to elucidate the ``sloppy reading puzzle''.	
\begin{itemize}
\item Phillip went to his office. Marcel didn't.
\end{itemize}
\item \textbf{This can mean either:} Marcel didn't go to Phillip's office, or he didn't go to his own office.
\item If both instances of the variable are free, then the pronoun will be interpreted according to context.
\begin{multicols}{2}	
\Tree	[.S
			[.Phillip ]
			[.	
				[.$\lbrack$\textsc{past}$\rbrack$ ]	
				[.VP
					[.{go to} ]
					[.{his_x office} ]
				]
			]
		]

\Tree	[.S
			[.Marcel ]	
			[.
				[.didn't ]
				[.$\langle$VP$\rangle$
					[.$\langle${go to}$\rangle$ ]
					[.$\langle${his_x office}$\rangle$ ]
				]
			]
		]
\end{multicols}	
\item The first free variable will be interpreted according to the context. If Phillip is the most salient entity it will refer to him. Additionally, H \& K argue that if a free variable is elided it cannot fail to co-refer with the the remnant free variable.
\item Referential pronouns keep their reference under ellipsis.  
\item Alternatively, both pronouns can be bound, leading to the reading that Marcel didn't go to his own office.
\end{itemize}
\begin{multicols}{2}	
\Tree	[.S
			[.$\lbrack$Phillip$\rbrack^x$ ]
			[.	
				[.$x$ ]	
				[.
					[.$\lbrack$\textsc{past}$\rbrack$ ]	
					[.VP
						[.{go to} ]
						[.{his_x office} ]
					]
				]
			]
		]

\Tree	[.S
			[.$\lbrack$Marcel$\rbrack^x$ ]
			[.	
				[.$x$ ]	
				[.
					[.didn't ]
					[.$\langle$VP$\rangle$
						[.$\langle${go to}$\rangle$ ]
						[.$\langle${his_x office}$\rangle$ ]
					]
				]
			]
		]
\end{multicols}	
\begin{itemize}
\item The Binding Principle predicts that the sloppy reading will be grammatical in just those cases where the pronoun is bound syntactically by a preceding anaphor. This indicates a bound variable at LF. 
\begin{itemize}
\item His father spoils Roman, but not Felix. 
\end{itemize}
\item \textbf{This cannot mean:} Roman's father spoils Roman but Felix's father doesn't spoil Felix.  
\item Additionally, Binding theory predicts that the ``strict'' reading will be impossible in cases where the pronoun must be bound, such as reciprocals.
\begin{itemize}
\item Ann hurt herself, and Mary (did) too.
\end{itemize}
\end{itemize}
			
\section{Syntactic and semantic binding}

H \& K tie semantic binding to QR:

\begin{tabular}{p{.5\linewidth} p{.5\linewidth}}
	\Tree [.S DP$_x$ [ {$\lambda x$} \qroof{\dots $t_x$\dots}.{} ] ]

	&
		\begin{tabular}{l}
			$t_x ~> g(x)$\\
			$x ~> \lambda p_{t}.\lambda x_e.p$\\
			DP$_x ~>$ DP$^{~>}$\\
			S $~> [DP$^{~>}$] (\lambda x_e.p)$ or $[\lambda x_e.p] (DP$^{~>}$)$
		\end{tabular}
	\\
\end{tabular}

\noindent In class, we allowed for semantic binding without QR:

\begin{tabular}{p{.5\linewidth} p{.5\linewidth}}
	\Tree [.S DP$^x$ \qroof{\dots $t_x$\dots}.{}  ]

	&
		\begin{tabular}{l}
			$t_x ~> g(x)$\\
			DP$_x ~>$ DP$^{~>}$\\
			S $~> [DP$^{~>}$] (\lambda x_e.p)$ or $[\lambda x_e.p] (DP$^{~>}$)$
		\end{tabular}
	\\
\end{tabular}



\begin{itemize}
	\item Suppose: indices of pronouns (and the variables they get translated to) are present in surface syntax.
	\item Rationalization: Index as condition for semantic interpretability of pronouns and condition for movement (will supply pronoun label for trace).
	\item Goal: Then we can talk about the relationship of syntactic and semantic binding.
\end{itemize}


\subsection{Syntactic binding:}

	\begin{itemize}
		\item c-command and coindexation
	\end{itemize}
	\begin{exe}
		\ex \label{synbind} \Tree [ {every diver$_x$}  [ defended themselves$_x$ ] ]
	\end{exe}
	\begin{itemize}
		\item The DP \lq {every diver$_x$}\rq\ \emph{syntactically binds} the reflexive pronoun \lq themselves$_x$\rq.
	\end{itemize}

\subsection{Semantic binding (H\&K):}
	\begin{itemize}
		\item Variable binding with operators:
		\item A DP $\alpha$ \emph{semantically binds} a DP $\beta$ iff the variable introduced as the referent of $\beta$ is bound by a variable binder introduced by $\alpha$.
		\item In (\ref{synbind}), \lq themselves$_x$\rq\ is not semantically bound in H\&K's theory. (No $\lambda$-abstraction without QR)
	\end{itemize}
	\begin{exe}
		\ex \label{sembind} \Tree [ {every diver$_x$} [ $\lambda x$ [ t$_x$  [ defended themselves$_x$ ] ] ] ]
	\end{exe}
	
\begin{itemize}
	% \item In H \& K, $\lambda$-abstraction requires QR. Accordingly, the pronoun themselves$_x$ is semantically bound in 
	\item A system that allows for $\lambda$-abstraction without QR and accounts for quantifier scope with type-shifting (and doesn't allow QR) predicts a tight correspondence between semantic and syntactic binding.
	\item In fact, we find that they semantic and syntactic binding correlate.
\end{itemize}

\subsection{Syntactic binding principles constrain interpretation}

\begin{exe}
	\ex Syntactic binding principles:
	\begin{xlist}
		\ex Reflexive (and reciprocal) pronouns must be bound in their binding domain.
		\ex All other pronouns must be free in their binding domain.
		\ex All non-pronominal DPs must be free.
	\end{xlist}
\end{exe}

\begin{itemize}
	\item No bound reading for proper names:
\end{itemize}

\begin{exe}
	\ex \emph{His father spoils Roman, but not Felix.}
\end{exe}

\begin{itemize}
	\item Bound or referential reading for pronouns. (Strict vs. sloppy identity):
\end{itemize}

\begin{exe}
	\ex \label{pron} \emph{On Roman's birthday Phillip went to his office. Marcel didn't.}
\end{exe}

\begin{itemize}
	\item Two possible readings for (\ref{pron}): Marcel went to Roman's office vs. Marcel went to Phillips office vs. Marcel went to his own office.
	\item Only bound reading for reflexives, i.e. sloppy identity.
\end{itemize}

\begin{exe}
	\ex \emph{Phillip hurt himself. Marcel didn't.}
\end{exe}
\begin{itemize}
	\item Only bound reading: Marcel didn't hurt himself. But not: Marcel didn't hurt Phillip.
	\item[$=>$] Syntactic and semantic binding have to coincide
	\item H\&K have to stipulate that as a constraint on QR
	\item But we see cross-over effects constraining overt kinds of syntactic movement as well
\end{itemize}




\subsection{Weak crossover}

\begin{exe}
	\ex \label{weakcr} \emph{*The shark next to him$_x$ attacked $[$every diver$]_x$.}
\end{exe}

\begin{itemize}
	\item The quantifier $[$every diver$]_x$ cannot bind him$_x$
	\item Constraint on QR: cannot move across co-indexed pronoun (cross-over)
\end{itemize}

% \begin{exe}
% 	\ex \emph{*The shark next to him$_x$ attacked $[$every diver$]_x$.}\\
% 	\begin{tikzpicture}
% 		\Tree [.S \node(1){$[$every diver$]x$}; [.S [ the [shark [next \node(3){to him$_x$}; ] ] ] [ attacked \node(2){t$_x$}; ] ] ]
% 		\node (s1) [below=1cm of 1] {};
% 		\node (s2) [below=1cm of 2] {};
% 		\draw[dotted, ->] (2)..controls +(south:5) and +(south:5)..(1) node[midway,below] {\tiny QR blocked};
% 		\node (s3) [below right=1cm of 3] {\tiny intervention};
% 		\draw (3.east) -- (s3);
% 	\end{tikzpicture}
% \end{exe}

\begin{exe}
	\ex \emph{*The shark next to him$_x$ attacked $[$every diver$]_x$.}\\
		\Tree [.S {$[$every diver$]x$} [.S [ the [shark [next {to him$_x$} ] ] ] [ attacked t$_x$ ] ] ]
\end{exe}

\vspace{2\baselineskip}
\begin{itemize}
	\item Evidence that semantic binding ($\lambda$-abstraction) requires syntactic binding (c-command + coindexation)
	\item However, we can get both scopal readings in a case like (\ref{weakcr}), better seen with a non-definite subject\\(e.g. (\ref{weakcramb}))
\end{itemize}

\begin{exe}
	\ex \label{weakcramb} \emph{One of the sharks next to him attacked every diver.}
\end{exe}

\begin{itemize}
	\item Two scope readings available without binding
	\begin{itemize}
		\item High scope ($\forall > 1$):\\
		$\forall y_e.(\textsc{diver}_{et}(y) \rightarrow \exists z.(\textsc{shark}_{et}(z) \land \textsc{next}_{eet}(x)(z) \land \textsc{attack}_{eet}(y)(z))) $\\
		True if every diver got attacked by at least one (potentially different) shark.

	\item Low scope ($1 > \forall$):\\
		$\exists z.(\textsc{shark}_{et}(z) \land \textsc{next}_{eet}(x)(z) \land \forall y_e.(\textsc{diver}_{et}(y) \rightarrow \textsc{attack}_{eet}(y)(z)))$\\
		True if one unique shark attacked every diver.
	\end{itemize}
	\item[$=>$] Untie quantifier scope from lambda abstraction
	\item[$=>$] Evidence that QR can't be the only way in which quantifiers take scope
	\item Type-lifting account can get the fact that the universal can scope high, but binding is not available:
	\item Consider for example the account with the high scoping accusative morpheme\\
	 (\textsc{acc}_2 $~>$  $\lambda Q_{(et)t}.\lambda R_{eet}. \lambda Q'_{(et)t}.Q(\lambda y_e.Q'(\lambda x_e.R(y)(x)))$)
\end{itemize}

\begin{exe}
	\ex \Tree [ [A [shark [next [to him$_a$ ] ] ] ] [attacked [\textsc{acc}$_2$ [ $[$every diver$]_b$ ] ] ] ]
\end{exe}

\begin{itemize}
	\item Subject DP lexical entries:\\

	\begin{tabular}{l c l}
		a 	 	& $~>$ 	& $\lambda P_{et}.\lambda P'_{et}.\exists x.(P(x) \land P^\prime(x))$ \\
		shark 	& $~>$ 	& $\textsc{shark}_{et}$\\
		next 	& $~>$ 	& $\textsc{next}_{eet}$\\
		to  	& $~>$ 	& $\lambda x_e.x$\\
		him$_a$	& $~>$ 	& $a_e$\\
	\end{tabular}



	\item Subject NP:\\

	$\Tree [shark [next [to him$_a$ ] ] ]  ~> \lambda x.\textsc{shark}_{et} \land \textsc{next}(a)(x)$ {\small(by predicate modification/$et$-conjunction)}



	\item Subject DP:\\

	$\Tree [a [shark [next [to him$_a$ ] ] ] ]$\\
	$~> \lambda P'_{et}.\exists x.(\textsc{shark}_{et} \land \textsc{next}(a)(x) \land P^\prime(x))$ 



	\item VP lexical entries:\\

	\begin{tabular}{l c l}
	  attacked 			& $~>$ 	& $\textsc{attack}_{eet}$\\
	  every 			& $~>$ 	& $\lambda P_{et}.\lambda P'_{et}.\forall y.(P(y) -> P'(y))$\\
	  diver 			& $~>$ 	& $\textsc{diver}_{et}$\\
	  \textsc{acc}_2 	& $~>$ 	& $\lambda Q_{(et)t}.\lambda R_{eet}. \lambda Q'_{(et)t}.Q(\lambda y_e.Q'(\lambda x_e.R(x)(y)))$\\
	\end{tabular}



	\item Object DP:\\

	$[$every diver$]_b ~> \lambda P'_{(et)t}. \forall y.(\textsc{diver}_{et}(y) -> P'(y))$

	\item Object DP with Case:\\

	$\Tree [\textsc{acc}$_2$ [ $[$every diver$]_a$ ] ] ~> \parbox{.7\textwidth}{$\lambda R_{eet}. \lambda Q'_{(et)t}.[\lambda P'_{(et)t}. \forall y.(\textsc{diver}_{et}(y) -> P'(y))](\lambda y_e.Q'(\lambda x_e.R(y)(x)))\\
	<=> \lambda R_{eet}. \lambda Q'_{(et)t}.\forall y.(\textsc{diver}_{et}(y) -> [\lambda y_e.Q'(\lambda x_e.R(y)(x))](y))\\
	<=> \lambda R_{eet}. \lambda Q'_{(et)t}.\forall y.(\textsc{diver}_{et}(y) -> Q'(\lambda x_e.R(y)(x)))
	$
	}$



	\item VP:\\

	$\Tree [attacked [\textsc{acc}$_2$ [ $[$every diver$]_a$ ] ] ] ~> \lambda Q'_{(et)t}.\forall y.(\textsc{diver}_{et}(y) -> Q'(\lambda x_e.\textsc{attack}_{eet}(y)(x)))$

	\item Putting it all together:\\
	A shark next to him attacked every diver.\\
	$~> [\lambda Q'_{(et)t}.\forall y.(\textsc{diver}_{et}(y) -> Q'(\lambda x_e.\textsc{attack}_{eet}(y)(x)))](\lambda P'_{et}.\exists x.(\textsc{shark}_{et} \land \textsc{next}(a)(x) \land P^\prime(x)))$
	\\$<=> \forall y.(\textsc{diver}_{et}(y) -> [\lambda P'_{et}.\exists x.(\textsc{shark}_{et} \land \textsc{next}(a)(x) \land P^\prime(x))](\lambda x_e.\textsc{attack}_{eet}(y)(x)))$
	\\$<=> \forall y.(\textsc{diver}_{et}(y) -> \exists x.(\textsc{shark}_{et} \land \textsc{next}(a)(x) \land [\lambda x_e.\textsc{attack}_{eet}(y)(x)](x)))$
	\\$<=> \forall y.(\textsc{diver}_{et}(y) -> \exists x.(\textsc{shark}_{et} \land \textsc{next}(a)(x) \land \textsc{attack}_{eet}(y)(x)))$

	\item High scope of object quantifier possible without c-command. Evidence in favor of a theory that allows quantifiers to scope high without movement.
\end{itemize}

\end{document}

%%% Local Variables:
%%% mode: xetex
%%% TeX-master: t
%%% TeX-engine: xetex
%%% End:
